\paragraph{0 THE FOOL} On the long journey through graduate school, there have been an immeasurable number of people who saw a twenty-one-year-old with little concept of how to debug code and helped shape her into a professor of computer science.

\paragraph{I THE MAGICIAN} To Arend Hintze, whose support of scientific failure shaped my outlook through my graduate career. 

\paragraph{II THE HIGH PRIESTESS} To Emily Dolson, who always let me cause a problem, celebrate our wins, and cry in her office.

\paragraph{III THE EMPRESS} To Mom and all the times you let me leave the nest.

\paragraph{IV THE EMPEROR} To Dad and long summers filled with riddles.

\paragraph{V THE HIEROPHANT} To Charles Ofria, larger than life and down to earth.

\paragraph{VI THE LOVERS} To the strange little tangle of joy and love I've found myself in: Shayne, and Parker, and Jess. 

\paragraph{VII THE CHARIOT} To Jory Schossau, who taught me, with equal patience, how to use vim and drive a car.

\paragraph{VIII STRENGTH} To the long, long list of people whose laughter kept me afloat---Brielle and Crook and Mei and Luisa and DT and Giants and Kitsey and too many more to name. 

\paragraph{IX THE HERMIT} To Elliott Whitson. There's no one else I'd rather be in a folie \`a deux with.

\paragraph{X THE WHEEL} To the undergraduates I've been fortunate enough to mentor these last few years: Sarah Albani, Aria Killebrew-Bruehl, and Lanea Rohan.

\paragraph{XI JUSTICE} To Grampy and Grammy and their magical home for wayward souls.

\paragraph{XII THE HANGED MAN} To Clifford Bohm, for the new worlds I got to play in.

\paragraph{XIII DEATH} To Harmony. I don't ask much from you, but I asked for this. Thank you.

\paragraph{XIV TEMPERANCE} To Elise Zipkin. Thank you for keeping the wheels on the track.

\paragraph{XV THE DEVIL} To Anya Vostinar. Let's crash the next train.

\paragraph{XVI THE TOWER} To the plague years. Good riddance.

\paragraph{XVII THE STAR} To Katie. What else is there to say after seven years?

\paragraph{XVIII THE MOON} To the remaining members of the Hintze lab and Devolab: Clifford Bohm, Douglas Kirkpatrick, Nitash CG, Vincent Ragusa, Alex Lalejini, Matthew Moreno, Jose Hernandez, Kate Skocelas, and Austin Ferguson. Thank you for being there through the different phases of my graduate career.

\paragraph{XIX THE SUN} To the members of the ECODE lab: Shakiba Shahbendegan, Austin Mills, Anna Catenacci, and Aria Kingstrom. Thank you for the warmth the last year.

\paragraph{XX JUDGEMENT} To my committee members, Ingo Braasch and Christoph Adami, who let me spin this together and was there weaving with me all the way.

\paragraph{XXI THE WORLD} Here's to the rest of the journey with you all.