\section{Domain Requirements and System Overview}

Based on the above literature, conversations with domain experts, and our own experience as active researchers in the field, we identified five key requirements for a new VR-based fitness landscape visualization and incorporated them into our final design.

\subsection{Requirements}

The following requirements were identified as essential to the design to meet the goal of gaining spatial insight into how fitness landscapes behave across dimensions.

\paragraph{\textbf{R1: Spatial Insight.}} Experts must get a sense of depth, distance, and scale within a three-dimensional space in order to build spatial intuition.

\paragraph{\textbf{R2: Ease of Access.}} Experts must have access to the visualization even without virtual reality hardware in order to increase reach and usability.

\paragraph{\textbf{R3: Ease of Interpretation.}} Experts must be able to interpret the visualization without drawing upon mathematical background knowledge.

\subsection{System Overview}

Tessevolve (\textbf{tess}eract $+$ e\textbf{volve}) is a web-enabled three dimensional fitness landscape visualization built to address the domain requirements listed above. With this visualization, we seek to expand intuitive understanding of crucial domain concepts such as landscape ruggedness and lineage traversal. We address R1 (Spatial Insight) by implementing the visualization in an established virtual reality framework which handles depth and distance. This framework is hooked into a web-enabled interface so as to be accessible through any internet connected device to address R2 (Ease of Access). Finally, we solicit and report qualitative feedback from experts on the intuitiveness of design to address R3 (Ease of Interpretation). 